Models

### 2023-02-13 Code/Models.Rmd
Added code

@@

@@

```{r}
t.test(comp$NineteenS, comp$TwentyTwoS, paired = TRUE)
clusWilcox.test(comp$NineteenS, cluster=comp$TwentyTwoS, paired = TRUE, alternative = "greater")
wilcox.test(comp$NineteenS, comp$TwentyTwoS, paired = TRUE)
```

>>>>

```{r}
men_finals_yeareffect <- lmer(RxnTime ~ (1|Year), data = men_finals)
men_finals_one <- glm(RxnTime ~ 1, data = men_finals)
anova(men_finals_one, men_finals_yeareffect)
AIC(men_finals_one)
AIC(men_finals_yeareffect)
summary(men_finals_yeareffect)
```
```{r}
logLik(men_finals_yeareffect)
logLik(men_finals_one)
```
```{}
For finals only data, the year effect is not helpful
```

```{r}
men_finals_yeareffect_log <- lmer(log(RxnTime) ~ (1|Year), data = men_finals)
men_finals_one_log <- glm(log(RxnTime) ~ 1, data = men_finals)
AIC(men_finals_yeareffect_log)
AIC(men_finals_one_log)
```
```{r}
men_final_yeareffect_gamma <- glmer(RxnTime ~ (1|Year), data = men_finals, family = Gamma)
men_final_one_gamma <- glm(RxnTime ~ 1, data = men_finals, family = Gamma)
AIC(men_final_yeareffect_gamma)
AIC(men_final_one_gamma)
logLik(men_final_yeareffect_gamma)
logLik(men_final_one_gamma)
```
```{}
Should not fit with normal, gamma is better and shows that the year effect is helpful.
Can try this again without last years data.
```

```{r}
old_final_yeareffect_gamma <- glmer(RxnTime ~ (1|Year), data = old_finals, family = Gamma)
old_final_one_gamma <- glm(RxnTime ~ 1, data = old_finals, family = Gamma)
AIC(old_final_yeareffect_gamma)
AIC(old_final_one_gamma)
logLik(old_final_yeareffect_gamma)
logLik(old_final_one_gamma)
summary(old_final_yeareffect_gamma)
summary(men_final_yeareffect_gamma)
```

```{}
Simulate to see what prob of a time less than 0.1 second rxn time.
```

@@

```{r}
library(lme4)
men_pooled_gamma_year <- glmer(RxnTime ~ (1 | Year), data = men_pooled, family = Gamma(link = "log"))
baseline <- glm(RxnTime ~ 1, data = men_pooled, family = Gamma(link = "log"))

simfit <- function(men_pooled_gamma_year, n = 12000000) {
  vc <- as.data.frame(VarCorr(men_pooled_gamma_year))
  ## mu <- exp(coef(men_pooled_gamma_year)$Year[,]) ## using fitted random effects only
  z <- rnorm(n, sd = vc$sdcor[1]) #$ using generated random effects
  mu <- exp(fixef(men_pooled_gamma_year) + z)
  shape <- 1 / vc$vcov[2]
  x <- rgamma(n, shape = shape, scale = mu / shape)
  x
}
sbaseline <- summary(baseline)
x <- simfit(men_pooled_gamma_year)
mean(x < 0.1)
quantile(x, prob = c(.00001, .0001, .0005, .001))
## compare with and without random effect
plot(density(x)) # with random effect
curve(dgamma(x, shape = 1 / sbaseline$dispersion,
             scale = exp(coef(baseline)) * sbaseline$dispersion),
      0.08, 0.22, add = TRUE, col = "blue") # fixed effect only
```
```{}
Every 1000 racers, we expect 7 to have a reaction time below 0.1 seconds.  If we want 1 out of every 1000
```

@@

```{r}
t.test(comp$NineteenS, comp$TwentyTwoS, paired = TRUE)
clusWilcox.test(comp$NineteenS, cluster=comp$TwentyTwoS, paired = TRUE, alternative = "greater")
wilcox.test(comp$NineteenS, comp$TwentyTwoS, paired = TRUE)
```
```{}
Cluster by 2019 and 2022
Columns: Athlete, RxnTime, 2019/2022
```
